Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fix in intro

Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
e \Downarrow_{*} o $), where an observation is a value constructor or a blame. 
Despite the striking similarity of these proves, they are all built from ground 
up. We present a framework for proving correctness of cast reprensentation 
(Section~\ref{sec:framework}), and use it to prove the correctness of 
hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
that this framework is general enough to include coercion and threesome.

>>>>

Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
e \Downarrow_{*} o $), where an observation is either a value constructor or 
blame. 
Despite the striking similarity of these proofs, they are all built from ground 
up. We present a framework for proving correctness of cast reprensentation 
(Section~\ref{sec:framework}), and use it to prove the correctness of 
hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
that this framework is general enough to include coercion and threesome.
